Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair

### 2017-06-05 paper/ms.tex
Restructure tex and paper
- Add text to discussion and summary.
- Move figures and paragraphs around.
- Figure captions enhanced.

Independently, in efforts to connect the host star's chemistry to
its planetary system, wide binaries with similar or very different planetary architectures around
the component stars are particularly useful as chemical signatures related to planet formation or accretion
can be revealed in a differential sense without any regard to the Galactic chemical evolution
as long as we assume that the two stars should have been born together with identical composition.
For close-in giant planets, it has been established that the planet-metallicity relation
is primordial, and that the enhanced metallicity in giant planet-hosting stars likely
promoted the formation of giant planets (\citealt{Fischer:2005aa}) by increasing
the availability of small particle condensates that forms planetesimals.
On the other hand, if host stars are to be polluted after their birth
by rocky planetary material with high refractory-to-volatile ratio,
the convective envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
compared to their initial state.
Thus, differing planet formation or accretion in the two otherwise identical stars
may imprint a difference of chemical abundances that depends on the
condensation temperature (\Tcondens).
Several systems in which at least one star hosts at least one planet
have been studied so far with high resolution spectroscopy in this context
(\citealt{Teske:2013aa,Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
  Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab}).
The results and interpretations of these studies are varied: while some systems
found no difference (see also \citealt{Desidera:2004aa,Gratton:2001aa}), other
studies  have found a \Tcondens-dependent difference in abundance.
The increasing difference of abundance with condensation temperature
has been attributed both to more yet-undiscovered rocky planets around
the relatively refractory-poor star and to late time accretion of
refractory-rich planetary material (\citealt{Ramirez:2015aa,Biazzo:2015aa}.
% maybe want to point out the former interpretation roots back to melendez+09
% and some doubt to that interpretation...

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaXH_elem_violins.pdf}
  \caption{Abundance difference in this pair and other twin-like
    ($\Delta T_\mathrm{eff}\lesssim 100$~K) wide binaries in
    \citealt{2016ApJS..225...32B}.
    The differences in other pairs are small ($<0.05$~dex)
    for all elements except \elem{N} and \elem{O} which are the most
    uncertain, making the difference of $\approx 0.2$~dex seen in
    \bizarreone-\sunanalog\ rare.
    Additionally, we show the distribution of abundance differences
    between stars with similar metallicity difference
    ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
    as violins with medians indicated by black line segments
    by randomly pairing up single stars in \citealt{2016ApJS..225...32B} at two metallicity bins,
    $-0.025 < \feh < 0.025$ (160 stars) and $1.975 > \feh > 2.025$ (137 stars),
    similar to \bizarreone\ and \sunanalog.
    The difference is always taken to be $\mathrm{higher}\,\feh - \mathrm{lower}\,\feh$.
    Thus, the narrower range of in $\Delta\feh$ is by construction.
    Random pairings of disk stars with similar $\Delta\feh$ usually show
    similar enhancement in all other elements
    unlike the pattern seen in \bizarreone-\sunanalog\ pair.
  }
  \label{fig:deltaXH}
\end{figure}

@@

We stress that none of the other four twin-like ($\Delta T_\mathrm{eff}
\lesssim 100$~K) wide binary pairs examined in \citealt{2016ApJS..225...32B}
show discrepancies in abundances between the stars at this level.
As shown in \figname~\ref{fig:deltaXH},
the differences in other pairs for all elements except \elem{N} and \elem{O},
which are also the most uncertain (\tablename~\ref{tab:kk})
are less than $0.05$~dex, makiing \bizarreone-\sunanalog\ pair an outlier.
Moreoever, the abundance differences cannot be due to different chemical enrichment
history in the disk even if the two stars were of different origin.
\figname~\ref{fig:deltaXH} additioanlly shows the distribution of $\Delta[\elem{X}/\elem{H}]$
for random pairings of two stars with similar \feh\ as \bizarreone\ and \sunanalog
as violins for each element.
We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
all other elements are enhanced at a similar level with some variations.
Specifically, for a typical star with $\elem{Fe} \approx 0.2$~dex,
we generally expect $[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
(\citealt{Battistini:2015aa,Bensby:2003aa})
making the low $\elem{Na}/\elem{Fe}$ and $\elem{Mn}/\elem{Fe}$ seen in \bizarreone\
very unlikely to arise from variations in Galactic chemical evolution.

@@

In fact, the surface lithium abundance is the only indication that points to younger ages.
If the two stars are indeed only several hundred Myrs old at most,
they are expected to be part of a larger comoving group of stars.
However, as we mention above, there is no evidence in our search of comoving pairs
using \tgas\ that the two stars belong to a larger group of young stars.
Very young stars are often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks.
We have looked for these signs for the pair to find none, and their spectral energy
distributions are consistent with blackbody.
The low $v\sin(i)$ values also argue against very young ages inferred from the
surface lithium abundances.
% TODO: reference for vertical action as age?
Finally, the pair's fiducial orbit in a axisymmeric Milky Way-like potential
has a vertical action larger than the Sun, favoring an older age.
We concluded that the two stars are most likely coeval, $\sim 4$~Gyr old main
sequence stars, and that their unusually high \elem{Li} abundance requires an
alternative explanation.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
  \caption{Abundance of \bizarreone\ ($[\mathrm{Fe}/\mathrm{H}] = 0.20$)
    relative to \sunanalog\ ($[\mathrm{Fe}/\mathrm{H}] = 0.01$)
    ranked by the condensation temperature of elements in solar composition gas
    from \citealt{2003ApJ...591.1220L}.
    We show three wide binary systems selected from the literature:
    HD~20782/1 (\citealt{Mack:2014aa}), XO-2N/S (\citealt{Biazzo:2015aa}),
    and WASP-94AB (\citealt{Teske:2016aa}).
    Note that multiple values are reported 
  }
  \label{fig:relabun_tcrank}
\end{figure}

@@

% binary-single and binary-binary exchange
Two stars unrelated at birth may end up in a binary system via binary-single scattering event
that results in an exchange of binary member.
In order to estimate the rate at which any binary-single
event will produce a wide binary system such as \sunanalog\ and \bizarreone,
we may consider the rate at which this wide binary will scatter with a field star to
result in an exchange reaction.
The cross-section of exchange scattering for a binary with semi-major axis $a$ is
\begin{eqnarray}
  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \frac{1}{v^6}
\end{eqnarray}
where $v$ is the incoming velocity $v_i$ in units of critical velocity $v_c$ defined as
\begin{eqnarray}
  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}
\end{eqnarray}
when $v \gg 1$ using the impulse approximation (\citealt{Hut:1983aa,Hut:1983ab}),
which is appropriate for wide binaries scattering with field (disk) stars.
If we assume that field stars are made of solar mass stars
with constant number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars
is $10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk
stars in any direction, the rate of exchange scattering is
\begin{eqnarray}
  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
  \frac{n}{\mathrm{pc}^3} \frac{\mathrm{pc}}{a} \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5
\end{eqnarray}
low enough to be negligible.
Because the exchange scattering cross section steeply depends on the incoming velocity
relative to the critical velocity (of the order of orbital velocity of the binary),
the rate of exchange scattering with a star within the same star forming region
may be much larger.
However, even in such scenario, the age difference of $\sim 500$~Myr is too large
for two stars of the same star forming region.

%LEIGH

%Two factors that make this even more unlikely are that both stars are very young given their large Li,
%and that if the pair is a result of scattering, one expect to end up with typical stars of the field,
%not HD30 with anomalous abundance patterns.

None of the above scenarios is satisfactory as they offer no
insight on the peculiarity of the abundances of \bizarreone\
(see \sectionname~{\ref{sec:data}}).
In case that the pair formed from a exchange scattering event,
we would expect the pair to be composed of typical field stars.
The unlikeliness of the above possibilities naturally leads us to
consider the alternative.
What can selectively enrich refractory (high $T_C$) elements
in one of the two stars that are born together?

% inhomogeneity in star formation
It may be that the two stars are born at the same time from the same cloud, but
there is inhomogeneity within the cloud.
However, there is already ample amount of evidence against such scenario.
First, none of the other seven similar wide binaries examined in \citealt{2016ApJS..225...32B}
show the same level differences in abundances although there is generally
a larger spread in $\elem{C}$, $\elem{N}$ and $\elem{O}$, and some pairs show
a large as $\approx 0.15$~dex difference in particular elements.
The median and maximum \feh\ difference between component stars in the other seven pairs
is $0.02$~dex and $0.09$~dex, respectively.
This is consistent with the findings of \citealt{Desidera:2004aa}, who examined 23 wide binaries
of late F to K dwarfs, and found most pairs show difference in \feh\ less than $0.02$~dex
and none larger than $0.07$~dex.

% rocky planets (or the like) engulfment
Yet another possibility that may change a star's surface abundance after formation
is accretion of its planets or asteroids.
Instabilities may develop in a multi-planet system due to chaotic
nature of many body system, which may lead to planet engulfment by the host star.

One informative proxy that may reveal the composition of the hypothetical material
that was accreted to the stars is the condensation temperature.

Present the relative abundance figure here

One can carry out simple toy calculations of expected $\Delta\elemH{X}$
in a Sun-like star's atmosphere when adding material of e.g., bulk Earth composition
under these assumptions:
\begin{itemize}
  \item The material added is instantly and completely mixed.
  \item The atmospheric composition that we measure is identical throughout
    the star's radiative and convective zone.
\end{itemize}
We take the solar abundances $\elemH{X}$ of \citealt{Asplund:2009aa}
which can be converted to mass fraction in each element $X$ as in
\begin{equation}
  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
\end{equation}
where $m_X$ is the mass of each element in e.g., atomic mass unit.
One can check that the \citealt{Asplund:2009aa} abundances
are consistent with mass fraction in \elem{H}, \elem{He} and metals
$X,\,Y,\,Z=0.757,\,0.249,\,0.0134$ as stated in that work.
Assuming a fraction of the star's convective zone in mass $f_\mathrm{CZ}$,
and that the added material has a total mass $M_\mathrm{add}$ and mass fraction in each
element $f_{X,\mathrm{add}}$,
the abundance difference is
\begin{equation}
  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star} + f_{X,\mathrm{add}}\,M_\mathrm{add}}
    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
\end{equation}
We take the composition of bulk Earth from a chondritic model of the Earth
(\citealt{mcdonough2001composition}) and CI chondrite from \citealt{2009LanB...4B...44L}.

Figure~\ref{fig:toycalc} shows the expected change of surface abundances in a
Sun-like star after $20~\mearth$ of material with composition of bulk Earth or
CI chondrite is added.
The CI chondrites are believed to have the closest in composition to the solar nebular.
Their composition closely matches that of the solar atmosphere except
Li, highly volatile ($\Tcondens < 250$~K) elements, and the noble gases.
Other groups of chondrites show differing level of variations from CI chondrites.
It has been long known that compared to CI or other carbonaceous chondrites,
the composition of the Earth shows a volatilaity trend that moderately volatile
elements (including Mn and Na) and volatile elements are incearsingly more
depleted with decreasing condensation temperature (\citealt{mcdonough2001composition}).
This trend is presumed to be closely related to the formation of terrestrial planets.
Given the simplistic assumptions laid out above, and the uncertainties
in our current knowledge of the compositions of terrestrial planets including bulk Earth,
the match between our toy calculation and the observed abundance difference
between \bizarreone\ and \sunanalog\ is remarkable.

>>>>

Independently, in efforts to connect the host star's chemistry to
its planetary system, wide binaries with similar or very different planetary architectures around
the component stars are particularly useful as chemical signatures related to planet formation or accretion
can be revealed in a differential sense without any regard to the Galactic chemical evolution
as long as we assume that the two stars should have been born together with identical composition.
For close-in giant planets, it has been established that the planet-metallicity relation
is primordial, and that the enhanced metallicity in giant planet-hosting stars likely
promoted the formation of giant planets (\citealt{Fischer:2005aa}) by increasing
the availability of small particle condensates that forms planetesimals.
On the other hand, if host stars are to be polluted after their birth
by rocky planetary material with high refractory-to-volatile ratio,
the convective envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
compared to their initial state.
Thus, differing planet formation or accretion in the two otherwise identical stars
may imprint a difference of chemical abundances that depends on the
condensation temperature (\Tcondens).
Several systems in which at least one star hosts at least one planet
have been studied so far with high resolution spectroscopy in this context
(\citealt{Teske:2013aa,Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
  Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab}).
The results and interpretations of these studies are varied: while some systems
found no difference (see also \citealt{Desidera:2004aa,Gratton:2001aa}), other
studies  have found a \Tcondens-dependent difference in abundance.
The increasing difference of abundance with condensation temperature
has been attributed both to more yet-undiscovered rocky planets around
the relatively refractory-poor star and to late time accretion of
refractory-rich planetary material (\citealt{Ramirez:2015aa,Biazzo:2015aa}).
% maybe want to point out the former interpretation roots back to melendez+09
% and some doubt to that interpretation...

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaXH_elem_violins.pdf}
  \caption{Abundance difference in this pair and other twin-like
    ($\Delta T_\mathrm{eff}\lesssim 100$~K) wide binaries in
    \citealt{2016ApJS..225...32B}.
    The differences in other pairs are small ($<0.05$~dex)
    for all elements except \elem{N} and \elem{O} which are the most
    uncertain, making the difference of $\approx 0.2$~dex seen in
    \bizarreone-\sunanalog\ rare.
    Additionally, we show the distribution of abundance differences
    between field stars with similar metallicity difference
    ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
    as violins with medians indicated by black line segments.
    These are random pairings of single stars in 
    in \citealt{2016ApJS..225...32B} at two metallicity bins,
    $-0.025 < \feh < 0.025$ (160 stars) and $1.975 > \feh > 2.025$ (137 stars),
    similar to \bizarreone\ and \sunanalog.
    The difference is always taken to be
    $\mathrm{higher}\,\feh - \mathrm{lower}\,\feh$.
    Thus, the narrower range of in $\Delta\feh$ is by construction.
    Random pairings of disk stars with similar $\Delta\feh$ usually show
    similar enhancement in all other elements
    unlike the pattern seen in \bizarreone-\sunanalog\ pair.
  }
  \label{fig:deltaXH}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{spec1.pdf}
  \caption{Selective segments of the spectra of \sunanalog\ and \bizarreone.
    Alternating sets of two rows show
    the continuum-normalized data and model in the upper panel,
    and the ratio (\bizarreone/\sunanalog) of data (gray) and model (black)
    in the lower panel.
  }
  \label{fig:spec1}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{spec2.pdf}
  \caption{Same as \figname~\ref{fig:spec1}
    but for smaller portions of spectra at longer wavelengths that are
    not dominated by \elem{Fe}.
    We mark elements that give rise to strong lines.
    The feature in the third column of the second row is a strong \elem{Li}
    line that was not modeled by \citealt{2016ApJS..225...32B}. This line was
    studied in a separate work (\citealt{jmlithium}).
    Note that the lines of \elem{Na} and \elem{O} which are under-enhanced
    in \bizarreone\ relative to \elem{Fe} or other refractory elements
    show weaker residuals.
  }
  \label{fig:spec2}
\end{figure}

@@

We stress that none of the other four twin-like ($\Delta T_\mathrm{eff}
\lesssim 100$~K) wide binary pairs examined in \citealt{2016ApJS..225...32B}
show discrepancies in abundances between the stars at this level.
As shown in \figname~\ref{fig:deltaXH},
the differences in other pairs for all elements except \elem{N} and \elem{O},
which are also the most uncertain (\tablename~\ref{tab:kk})
are less than $0.05$~dex, makiing \bizarreone-\sunanalog\ pair an outlier.
Moreoever, the abundance differences cannot be due to different chemical enrichment
history in the disk even if the two stars were of different origin.
\figname~\ref{fig:deltaXH} additioanlly shows the distribution of $\Delta[\elem{X}/\elem{H}]$
for random pairings of two stars with similar \feh\ as \bizarreone\ and \sunanalog\
as violins for each element.
We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
all other elements are enhanced at a similar level with some variations.
Specifically, for a typical star with $\elem{Fe} \approx 0.2$~dex,
we generally expect $[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
(\citealt{Battistini:2015aa,Bensby:2003aa})
making the low $\elem{Na}/\elem{Fe}$ and $\elem{Mn}/\elem{Fe}$ seen in \bizarreone\
very unlikely to arise from variations in Galactic chemical evolution.

@@

In fact, the surface lithium abundance is the only indication that points to younger ages.
If the two stars are indeed only several hundred Myrs old at most,
they are expected to be part of a larger comoving group of stars.
However, as we mention above, there is no evidence in our search of comoving pairs
using \tgas\ that the two stars belong to a larger group of young stars.
Very young stars are often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks.
We have looked for these signs for the pair to find none, and their spectral energy
distributions are consistent with blackbody.
The low $v\sin(i)$ values also argue against very young ages inferred from the
surface lithium abundances.
% TODO: reference for vertical action as age?
Finally, the pair's fiducial orbit in a axisymmetric Milky Way-like potential
has a vertical action larger than the Sun, favoring an older age.
We concluded that the two stars are most likely coeval, $\sim 4$~Gyr old main
sequence stars, and that their unusually high \elem{Li} abundance requires an
alternative explanation.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
  \caption{Abundance difference of \bizarreone-\sunanalog\ pair
    ranked by the condensation temperature of elements for solar composition gas
    from \citealt{2003ApJ...591.1220L}.
    The condensation temperature may be read from the gray line and right y-axis.
    We show three wide binary systems selected from the literature:
    HD~20782/1 (\citealt{Mack:2014aa}, $\feh\approx0$),
    XO-2N/S (\citealt{Biazzo:2015aa}, $\feh\approx0.35$),
    and WASP-94AB (\citealt{Teske:2016aa}, $\feh\approx0.3$).
    Locations of elements with at least one measurement from any study
    are indicated by a vertical line and its symbol.
    Note that often multiple values are reported for one element corresponding
    to different ionization states in equivalent width analyses.
    No other pair studied so far were shown to have such large difference
    in metallicity or sharp contrast between (moderately-)volatile and
    refractory elements as \bizarreone-\sunanalog.
  }
  \label{fig:relabun_tcrank}
\end{figure}

@@

% binary-single and binary-binary exchange
Two stars unrelated at birth may end up in a binary system via binary-single scattering event
that results in an exchange of binary member.
In order to estimate the rate at which any binary-single
event will produce a wide binary system such as \sunanalog\ and \bizarreone,
we may consider the rate at which this wide binary will scatter with a field star to
result in an exchange reaction.
The cross-section of exchange scattering for a binary with semi-major axis $a$ is
\begin{eqnarray}
  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \frac{1}{v^6}
\end{eqnarray}
where $v$ is the incoming velocity $v_i$ in units of critical velocity $v_c$ defined as
\begin{eqnarray}
  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}
\end{eqnarray}
when $v \gg 1$ using the impulse approximation (\citealt{Hut:1983aa,Hut:1983ab}),
which is appropriate for wide binaries scattering with field (disk) stars.
If we assume that field stars are made of solar mass stars
with constant number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars
is $10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk
stars in any direction, the rate of exchange scattering is
\begin{eqnarray}
  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
  \frac{n}{\mathrm{pc}^{-3}} \frac{\mathrm{pc}}{a} \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5
\end{eqnarray}
low enough to be negligible.
Because the exchange scattering cross section steeply depends on the incoming velocity
relative to the critical velocity (of the order of orbital velocity of the binary),
the rate of exchange scattering with a star within the same star forming region
may be much larger.
However, this, or any other exchange scattering scenario,
is still unsatisfactory as it offers no insight on the
peculiarity of the abundances of \bizarreone\ (see
\sectionname~{\ref{sec:data}}).
In case that the pair formed from an exchange scattering event,
we would expect the pair to be composed of typical field stars,
not one with such low $\elem{Na}/\elem{Fe}$ and $\elem{Mn}/\elem{Fe}$.

%LEIGH to fill in binary-binary exchange scattering?

The unlikeliness of the above possibilities naturally leads us to consider the
alternative that their peculiar disparity in chemical abundance space may be
more naturally explained.

% inhomogeneity in star formation
It may be that the two stars are born at the same time from the same cloud, but
there is chemical inhomogeneity within the cloud.
However, there is already ample amount of evidence against such scenario.
First, none of the other seven similar wide binaries examined in
\citealt{2016ApJS..225...32B} show the same level differences in abundances
although there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
$\elem{O}$, and some pairs show a large as $\approx 0.15$~dex difference in
particular elements.
The median and maximum \feh\ difference between component stars in the other
seven pairs is $0.02$~dex and $0.09$~dex, respectively.
The differences are even smaller (maximum $\Delta\feh = 0.03$~dex)
if we compare only twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) pairs.
This is consistent with the findings of \citealt{Desidera:2004aa}, who examined
23 wide binaries of late F to K dwarfs, and found most pairs show difference in
\feh\ less than $0.02$~dex and none larger than $0.07$~dex.
Similarly \citealt{Gratton:2001aa} found that four out of six equal mass binaries
have the same chemical composition with $\gtrsim 0.01$~dex uncertainties.
Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair
cannot be due to chemical inhomogeneity in the birth cloud.

% rocky planets (or the like) engulfment
Yet another more exotic possibility is that a star's surface abundance may
be altered by accretion of planetary material after birth.
Instabilities may develop in a multi-planet system due to its chaotic nature
which may lead to planet engulfment or ejection by the host star.
%TODO: needs references
% kozai?
Indeed, it is an important goal of many exoplanet studies
to detect chemical signatures of planet formation or accretion,
distinguish them from Galactic chemical evolution, and
connect them to theories of evolution of planetary systems.
One approach that is free from confusion with Galactic chemical evolution
is to compare two almost identical stars in a wide binary system,
which are assumed to be born together.

%One proxy that is informative of the composition of the material
%that was hypothetically accreted to a star is the condensation temperature (\Tcondens).
% TODO: why?

Only a handful of wide binary systems have been studied with high-resolution
spectroscopy in their detailed chemical abundances so far.
These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
We first review and summarize the studies of these systems focusing on key
characteristics of stars and planets, and interpretation of any trend in
$\Delta\elemH{X}$.
These studies commonly look for
%TODO: needs to include **16 Cyg** and HD~133131AB

{\bf HD~20782/HD~20782:} 
\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf
stars (G2/G9.5) with a projected separation of $\sim9000$~AU (corresponding to
4.2~arcmin sky separation). Both stars in this system host close-in giant
planets.
HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
Neptune-mass planets within 0.3~AU with moderately high eccentricity
($e\sim0.1-0.3$) \footnote{
  The two stars were monitored by \project{HARPS}
  campaign, and it has recently been reported by \citealt{} that HD~20781 hosts
  four planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le
  0.11$ within $\approx 0.35$~AU.}.
They found that the abundances of 15 elements between the two stars are
consistent with each other.
However, they argued that there is a moderately significant ($\sim 2\sigma$)
positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
of their measurements).
They interpreted that this slope may be evidence for accretion of
$10-20$~\mearth\ of H-depleted rocky material that were pushed in during giant
planet migration.

{\bf HAT-P-1:}
HAT-P-1 is a pair of G0 stars separated 11\arcsec\ apart in sky
with $\feh\approx0.15$.
The secondary star in the system is known to host one transiting giant planet
while no planet has been discovered around the primary star.
\citealt{Liu:2014aa} found that the two stars are identical in their
atmospheric composition: \feh\ is $0.146 \pm 0.014$ and $0.155 \pm 0.007$ for
the primary and secondary respectively, and $\Delta\elem{X}/\elem{Fe}$ is
consistent with zero for 23 elements measured with the mean error being
$0.013$~dex.
Based on this analysis, they concluded that the presence of close-in giant planet
does not necessarily lead to stellar atmospheric pollution of the host star.

{\bf HD~80606/HD~80607:}
A pair of G5 stars with super-solar metallicity ($\feh \approx 0.35$),
HD 80606/HD 80607, has been independently studied by
\citealt{Saffe:2015aa} and \citealt{Mack:2016aa} using the same KECK HIRES
spectra. HD 80606 hosts a giant planet with mass of $4~\mjupiter$ at $0.5$~AU
on a very eccentric ($e\approx0.95$) orbit while HD 80607 has no detected
planets.
Both studies have concluded that there is no significant
chemical difference between the two stars similar to the case of HAT-P-1.

The system was first analyzed by \citealt{Teske:2013aa}, who examined and found
essentially no significant difference in Fe, Ni, C, and O between the two
stars.
However, re-analysis of the system by the same authors using the same data in
\citealt{Teske:2015aa} found that the trend of $\Delta\elemH{X}$ with
\Tcondens\ varies significantly depending on the stellar parameters chosen in
their analysis. Both analyses were based on spectra
using Subaru High Dispersion Spectrograph at spectral resolution $R=60000$
covering $4450-5660$~\AA\ and $5860-7100$~\AA\ with S/N of $170-230$
(\citealt{Teske:2013aa}).

Independently, \citealt{Ramirez:2015aa} used Keck HIRES spectra ($R=67000$,
$4080-8300$~\AA) of the component stars with S/N of $350$ (in $5000-7500$~\AA)
to perform a differential abundance analysis.
They find that all 23 elements including Fe are enhanced in XO-2N
compared to XO-2S, and that the difference $\Delta\elemH{X}$ shows
a significant correlation with \Tcondens.
At low \Tcondens, volatile elements differ by $0.015$~dex
while the range of difference spans upto $0.1$~dex at $\Tcondens>1600$~K.
There are inconsistencies in the determination of stellar parameters
(\teff\ and \logg) between spectroscopic (based on Fe I/II lines)
and photometric analysis,
but the existence of correlation between $\Delta\elem{H}$ and
\Tcondens\ seems robust.

\citealt{Ramirez:2015aa} argued that the {\it depletion} of volatile elements
in XO-2S relative to XO-2N is plausibly due to the presence of {\it more} gas
giant planets around XO-2S, following a similar interpretation of
\citealt{Melendez:2009aa} of the trend between solar twins and the Sun.
In this scenario, forming planets in the protoplanetary disk are supposed to
``lock'' heavier elements to the core of gas giant planets as well as some
volatile elements in their envelopes. Then, the host star will accrete {\it
  gas} depleted in metals compared to their protostellar condition.
By tuning the metal content ($Z/X$) of gas giant planets and when the accretion
of gas occurs in terms of how much mass is in the convective envelop then, they
can match the mass difference of gas giant planets around each star, which is
at least $1~\mjupiter$.
On the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
\citealt{Ramirez:2015aa} estimated that $20~\mearth$ of equal-part mixture of
Earth and CM chondrite-like material can explain the trend either as refractory
{\it depletion} in XO-2S due to {\it more} rocky planets around XO-2S, or
refractory enhancement in XO-2N by late time accretion in which case the
complete opposite would be true.

{\bf WASP-94A/WASP-94B:} 
\citealt{Teske:2016aa} studied WASP-94A/WASP-94B, a pair of F8 and F9 stars
with super-solar metallicity ($\feh\approx 0.3$ for both stars). Both stars
host a hot Jupiter.
The planet hosted by WASP-94A is transiting with a misaligned, probably
retrograde circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little
more massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host
star.
With a claimed median uncertainty of $0.006$~dex among all elements, they
detected a depletion of volatile and moderately volatile ($\Tcondens < 1200$~K)
elements at $0.02$~dex level and an enhancement in refractory ($\Tcondens >
1200$~K) elements at $0.01$~dex level in WASP-94A relative to WASP-94B.
Excluding K, which is based on one strong line and largely affected by non-LTE
effect, their analysis shows a statistically significant non-zero slope between
$\Delta\elemH{X}$ and $\Tcondens$\footnote{
  %TODO: double check the following statement
  Note that the condensation
  temperature $\Tcondens$ used is for solar system composition
  gas, which can differ from that of higher metallicity gas.}.
They considered multiple possibilities related to the formation and evolution
of planetary systems around each star as well as causes unrelated to planets
such as dust cleansing during the fully convective phase or different rotation
and granulation between the stars, but did not favor any particular one.

We now turn to \bizarreone-\sunanalog\ pair.
In Figure~\ref{fig:relabun_tcrank}, we show the abundace difference
between \bizarreone\ and \sunanalog\ ordered by the rank of \Tcondens\
of each element.
The equilibrium condensation temperatures for the composition of solar system
are taken from \citealt{2003ApJ...591.1220L} (Table~8).
The difference seen in \bizarreone-\sunanalog\ is
compared to HD~20781/2, XO-2N/S, WASP-94A/B in \figname~\ref{fig:relabun_tcrank}.
The metallicity difference of $\approx 0.2$~dex observed in this pair
is larger than the differences seen in any other pairs studied so far.
%Indeed, some may consider such large difference in metallicity
%enough to concluded that the two stars are completely unrelated.
Strikingly, the five under-enhanced elements in \bizarreone\
relative to \sunanalog\ are the five most volatile in all elements measured.
The difference in \elem{Mn} ($\Tcondens = 1158$~K) and
\elem{Cr} ($\Tcondens = 1296$~K) suggests a break in $\Tcondens \approx 1200$~K.
This $\Tcondens$-dependent trend of $\Delta\elemH{X}$,
combined with the enhanced $\elem{Li}$ abundance ($A(\elem{Li}) = 2.75$),
strongly suggests that accretion of rocky material has occured in \bizarreone.

How much mass of rocky material is needed to explain an increment of $\approx 0.2$~dex?
One can carry out simple toy calculations of expected $\Delta\elemH{X}$
in a Sun-like star's atmosphere when adding material of e.g., bulk Earth composition
under these simplifying assumptions:
\begin{itemize}
  \item The material added is instantly and completely mixed.
  \item The atmospheric composition that we measure is identical throughout
    the star's radiative and convective zone.
  \item The surface abundance of the star has been altered once only by this
    accretion event, and remained the same since.
\end{itemize}

We take the solar abundances $\elemH{X}$ of \citealt{Asplund:2009aa}
which can be converted to mass fraction in each element $X$ as in
\begin{equation}
  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
\end{equation}
where $m_X$ is the mass of each element in e.g., atomic mass unit.
One can check that the \citealt{Asplund:2009aa} abundances
are consistent with mass fraction in \elem{H}, \elem{He} and metals
$X,\,Y,\,Z=0.757,\,0.249,\,0.0134$ as stated in that work.
Assuming a fraction of the star's convective zone in mass $f_\mathrm{CZ}$,
and that the added material has a total mass $M_\mathrm{add}$ and mass fraction in each
element $f_{X,\mathrm{add}}$,
the abundance difference is
\begin{equation}
  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star} + f_{X,\mathrm{add}}\,M_\mathrm{add}}
    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
\end{equation}
We take the composition of bulk Earth from a chondritic model of the Earth
(\citealt{mcdonough2001composition}).

Figure~\ref{fig:toycalc} shows the expected change of surface abundances of
metals in a Sun-like star after $20~\mearth$ of material with composition of
bulk Earth is added.
It has been long known that compared to CI or other carbonaceous chondrites,
the composition of the Earth shows a volatilaity trend that moderately volatile
elements (including Mn and Na) and volatile elements are incearsingly more
depleted with decreasing condensation temperature
(\citealt{mcdonough2001composition}).
This trend is presumed to be closely related to the formation of terrestrial
planets in particular to the radial temperature gradient in a protoplanetary
disk.
Given the simplistic assumptions laid out above, and the uncertainties in our
current knowledge of the compositions of terrestrial planets including bulk
Earth, the match between our toy calculation and the observed abundance
difference between \bizarreone\ and \sunanalog\ is remarkable.
